Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
A.B. review: calm down wording for svm win

FIXME: Add refs
There were few environmental modeling studies only in recent years in which SVM outperformed other models that clearly.
The absolute difference of around three percentage points is also worth noting:
We could not find a study in which SVM came out as the best model in such clear way.
All of these statements are based on the assumption that a proper hyperparameter tuning was conducted for all models (which we also claim for ourselves in this study).

>>>>

FIXME: Add refs when SVM was clearly worse then other algs.
In other (environmental) studies in recent years, SVM showed most often less good performances and was not able to outperform competing algorithms such as RF.
The difference to the second best performing model of around three percentage points is also worth noting:
We are not aware of a study in which SVM ranked as the best model that clearly.
All of these statements are based on the assumption that a proper hyperparameter tuning was conducted for all models (which we also claim for ourselves in this study).
